R Notebook

### 2017-03-30 doc/RMD/data-comparison.Rmd
update comparison

>>>>

### Sydney's comments

We have no clue why 805 is flagged. The changes to the metadata are correct.
The change from BL to FR was because of confusion between the source of the 
collectors vs. source of isolate.

TS was grouped into AU because it was too small of a sample size to do anything.

From here on out, we will use Sajeewa's data for analysis.
